Russian sanctions figures

### 2024-02-29 ms-russia-figures.Rmd
add two new species min/max plots

p_joined <- ggarrange(p1, p2, p3, ncol = 1)

@@

# Stats
chn_to_usa %>% 
  filter(year == 2020, 
         sciname %in% c("gadus chalcogrammus", "gadus morhua", "oncorhynchus gorbuscha"))

>>>>

p4 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
         year > 1996) %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "melanogrammus aeglefinus") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian haddock via China") +
  theme_bw()

p5 <- artis %>%
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN", importer_iso3c == "USA",
         year > 1996) %>%
  group_by(year, sciname) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>% 
  filter(sciname == "gadus macrocephalus") %>%
  left_join(chn_to_usa %>%
              select(year, sciname, min_russia, max_russia)) %>% 
  ggplot(aes(x = year)) +
  geom_ribbon(aes(ymin = min_russia, ymax = max_russia), fill = "#86ADA7", alpha = 0.5) +
  geom_line(aes(y = live_weight_t)) +
  labs(x = "", y = "tonnes, live weight", title = "US imports of Russian Pacific cod via China") +
  theme_bw()

p_joined <- ggarrange(p1, p2, p3, p4, ncol = 1)

@@

# Stats
chn_to_usa %>% 
  filter(year == 2020, 
         sciname %in% c("gadus chalcogrammus", "gadus morhua", "oncorhynchus gorbuscha", "gadus macrocephalus"))

consumption %>%
  filter(consumer_iso3c == "USA", source_country_iso3c == "RUS", year %in% 2015:2019) %>%
  group_by(sciname_hs_modified) %>% 
  summarise(consumption_live_t = sum(consumption_live_t)) %>% 
  arrange(desc(consumption_live_t)) %>%
  ungroup() %>%
  mutate(percent = 100*consumption_live_t/sum(consumption_live_t)) %>%
  mutate(cum_percent = cumsum(percent))
